---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tidyRSS)](https://cran.r-project.org/package=tidyRSS)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/tidyRSS)](https://CRAN.R-project.org/package=tidyRSS)
[![CRAN_Download_Badge](http://cranlogs.r-pkg.org/badges/grand-total/tidyRSS)](https://CRAN.R-project.org/package=tidyRSS)

tidyRSS is a package for extracting data from [RSS feeds](https://en.wikipedia.org/wiki/RSS), including Atom feeds and JSON feeds. For geo-type feeds, see the section on changes in version 2 below, or jump directly to [tidygeoRSS](https://github.com/RobertMyles/tidygeoRSS), which is designed for that purpose.  

It is easy to use as it only has one function, `tidyfeed()`, which takes four arguments:  

- the url of the feed; 
- a logical flag for whether you want the feed returned as a tibble or a list containing two tibbles; 
- a logical flag for whether you want HTML tags removed from columns in the dataframe; 
- and a config list that is passed off to [`httr::GET()`](https://httr.r-lib.org/reference/config.html).   



## Installation

It can be installed directly from CRAN with: 

```{r, eval=FALSE}
install.packages("tidyRSS")
```


The development version can be installed from GitHub with the [remotes](https://github.com/r-lib/remotes) package: 
```{r, eval = F}
remotes::install_github("robertmyles/tidyrss")
```


## Usage 

Here is how you can get the contents of the [R Journal](https://journal.r-project.org/): 

```{r, eval = FALSE}
library(tidyRSS)

tidyfeed("http://journal.r-project.org/rss.atom")
```

## Changes in version 2.0.0

The biggest change in version 2 is that tidyRSS no longer attempts to parse geo-type feeds into [sf](https://github.com/r-spatial/sf/) tibbles. This functionality has been moved to [tidygeoRSS](https://github.com/RobertMyles/tidygeoRSS). 

## Issues 

XML feeds can be finicky things, if you find one that doesn't work with `tidyfeed()`, feel free to create an [issue](https://github.com/robertmyles/tidyrss/issues) with the url of the feed that you are trying. Pull Requests are welcome if you'd like to try and fix it yourself.  


## Related  

There are two other related packages that I'm aware of:  

- [rss](https://github.com/noahhl/r-does-rss)
- [feedeR](https://github.com/DataWookie/feedeR)

In comparison to feedeR, tidyRSS returns more information from the RSS feed (if it exists), and development on rss seems to have stopped some time ago.  

# Other 

For the schemas used to develop the parsers in this package, see:   

- RSS: [https://validator.w3.org/feed/docs/rss2.html](https://validator.w3.org/feed/docs/rss2.html)  
- Atom: [https://validator.w3.org/feed/docs/atom.html](https://validator.w3.org/feed/docs/atom.html)  
- JSON: [https://jsonfeed.org/version/1](https://jsonfeed.org/version/1)  

